Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
added fractional weight references

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps for the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors.

@@

Before proving three lemmas that allow us to inductively add points to the support of a divisor (i.e. $\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  This will be used in three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
and $R_{\halfcan}$ minimally generated by $y_1, \ldots, y_n$ over 
$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
\begin{enumerate}
\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item $T\succ S\succ k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ succeed all monomials in $S$ which succeed all monomials in $k[x_1, \ldots, x_n]$)
\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	S \; \cup\; \langle T\rangle \; \cup \; \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
\end{align*}
\end{enumerate}
Then,
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
	+ \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
First, notice that $I'\subseteq I$ so 
\[
	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
\]

@@

To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
\begin{defn}
Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.  Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$. \todo{Do we need to instantiate the $z_i$.  If so, what is the best way to do so.  Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows: 
If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord_P(f) < -\ord_P(g)$
\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i > r_i$ for the largest $i$ such that $q_i\ne r_i$
\end{enumerate}
\end{defn}
\noindent One can easily verify graded $P$-lex these satisfy the conditions of an ordering.

Before stating the Lemma \ref{lem:sat-1}, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}. \todo{Peter: This sentence is very ugly.  On the other hand, I feel we need to say something about O'Dorney before the following definition, or else it is completely unmotivated.  How should we state it better?  Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.}

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha},
\end{equation}
and let
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then,

@@

\item[(b)] Choose an ordering $\prec$ on $k[u, x_1, \ldots, x_m]$ such that
\[
	\ord_u(f) < \ord_u(g) \implies f\prec g.
\]
Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order on $y_1, \ldots, y_n$ precedence over that on $u, x_1, \ldots, x_m$.  
If $I'$ and $I$ are the ideal of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then

@@

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$.  \todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.  On the other hand, the other parts already have a lot of information written down (especial part (b)), so its not clear where it should be put.  Maybe in a remark after the lemma?}
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}
\begin{proof}
By
Equation ~\ref{eqn:deg1-sat-ind}, for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.  We have already shown $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving us condition \ref{lem:relations_from_generators_induction}(1).  Our choice of order for monomials in $k[y_1, \ldots, y_n]$ and block order for those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).

Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.  Therefore, $f\in k[u, y_1, \ldots, y_n]$.  We note that $S$ generates $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.  That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup V \cup \{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]. 
\]
\todo{is $\{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]$ appropriate notation to mean all possible products between some $y_j\in \{y_1, \ldots, y_n\}$ and some element in $k[u, y_1, \ldots, y_n]$?}
Thus, we see that if $f\in k[u, y_1, \ldots, y_n]$, then $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{Z}_{\ge 0}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.  For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.  If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...}, and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.  We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_h$.  Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
\end{align*}
This gives us condition \ref{lem:relations_from_generators_induction}(3).  Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we prove (b) of this lemma.  \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.  On the other hand, it is somewhat important.  Should it be included?}

@@

\begin{rem}\label{rem:quad-gen}
If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i P_i}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
\end{rem}

\begin{rem}\label{rem:sat-1-gen-lem-generic}
The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).  When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
\end{rem}

We now restrict our attention to log canonical rings of stacky curves.  Lemma \ref{lem:sat-1} accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.  We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated at degrees two and three.

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in
		\{3, 4\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements
		$y_3, y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grevlex$ so that $y_3 \prec 
		y_4$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order with $x_2, \ldots, x_m$ preceding $y_3, y_4$.  Then
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
		\end{align*}
	%\item[(c)] Any set of minimal generators for $I'$ together with 
		%any set of relations with leading terms as in (b) minimally 
		%generate $I$.
\end{enumerate}
\end{lem}

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx, iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements $y
		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grevlex$ so that $y_3 \prec 
		y_4 \prec y_5$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block order so that $x_3, \ldots, x_m$ precede $y_3, y_4, y_5$.  Then,
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I) k[x, y_3, y_4, y_5] \\
			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5\rangle.
		\end{align*}
	%\item[(c)] Any set of generators for $I'$ together with 
	%	any set of relations with leading terms as in (b) 
	%	generate $I$.
\end{enumerate}
\end{lem}

@@

\begin{rem}
\label{rem:raise-fractional-order}
It is no coincidence that the proofs of Lemma ~\ref{lem:raise-stacky-order} and \cite[Theorem 8.5.7]{vzb:stacky} are almost identical. In fact, the proofs of both results can easily be generalized generalized to the case of fractional canonical divisors, that is $L \in \di X$ with $nL \sim K$, for any $n \in \BZ_{\geq 1}$.
\end{rem}

>>>>

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps in the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors.

@@

Before proving three lemmas that allow us to inductively add points to the support of a divisor (i.e. $\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  This will be used in the subsequent three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
and $R_{\halfcan}$ minimally generated by $y_1, \ldots, y_n$ over 
$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
\begin{enumerate}
\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	S \; \cup\; \langle T\rangle \; \cup \; \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
\end{align*}
\end{enumerate}
Then,
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
	+ \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
First, notice that $I'\subseteq I$ so 
\[
	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
\]

@@

To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
The following definition provides the necessary ordering for the subsequent lemma (Lemma \ref{lem:sat-1}).
\begin{defn}
Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.  Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$. \todo{Do we need to instantiate the $z_i$.  If so, what is the best way to do so.  Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows: 
If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
\end{enumerate}
\end{defn}
\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.

Before stating the subsequent lemma, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}. \todo{Peter: This sentence is very ugly.  On the other hand, I feel we need to say something about O'Dorney before the following definition, or else it is completely unmotivated.  How should we state it better?  Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.}

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\sigma$ for some $\sigma\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha},
\end{equation}
and let
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then,

@@

\item[(b)] Choose an ordering $\prec$ on $k[u, x_1, \ldots, x_m]$ such that
\[
	\ord_u(f) < \ord_u(g) \implies f\prec g.
\]
Equip $k[y_1, \ldots, y_n]$ with graded P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order on $y_1, \ldots, y_n$ precedence over that on $u, x_1, \ldots, x_m$.  
If $I'$ and $I$ are the ideal of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then

@@

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \sigma)$.  \todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.  On the other hand, the other parts already have a lot of information written down (especial part (b)), so its not clear where it should be put.  Maybe in a remark after the lemma?}
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}
\begin{proof}
By
Equation ~\ref{eqn:deg1-sat-ind}, for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.  We have already shown $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving us condition \ref{lem:relations_from_generators_induction}(1).  Our choice of order on monomials in $k[y_1, \ldots, y_n]$ and block order on those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\prec S\prec k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).  Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, so for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.  Therefore, $f\in k[u, y_1, \ldots, y_n]$.  We note that $S$ generate $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.  That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup V \cup \{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]. 
\]
\todo{is $\{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]$ appropriate notation to mean all possible products between some $y_j\in \{y_1, \ldots, y_n\}$ and some element in $k[u, y_1, \ldots, y_n]$?}
We see that we can write $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{J}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.  For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.  If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...}, and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.  We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_r$.  Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U-i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
\end{align*}
This gives us condition \ref{lem:relations_from_generators_induction}(3).  Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we get (b) of this lemma.  \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.  On the other hand, it is somewhat important.  Should it be included?}

@@

\begin{rem}\label{rem:quad-gen}
If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
\end{rem}

\begin{rem}\label{rem:sat-1-gen-lem-generic}
The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).  When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
\end{rem}

We now restrict our attention to log canonical rings of stacky curves.  The previous lemma accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.  We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated at degrees two and three.

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in
		\{3, 4\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements
		$y_3, y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order with $y_3, y_4$ preceding $x_2, \ldots, x_m$.  Then
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
		\end{align*}
	%\item[(c)] Any set of minimal generators for $I'$ together with 
		%any set of relations with leading terms as in (b) minimally 
		%generate $I$.
\end{enumerate}
\end{lem}

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx, iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements $y
		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
		y_4 \prec y_3$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block order so that $y_3, y_4, y_5$ precede $x_3, \ldots, x_m$.  Then,
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I) k[x, y_3, y_4, y_5] \\
			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5\rangle.
		\end{align*}
	%\item[(c)] Any set of generators for $I'$ together with 
	%	any set of relations with leading terms as in (b) 
	%	generate $I$.
\end{enumerate}
\end{lem}

@@
